\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black' (LOAD BEFORE STYLE)
\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'


% Github link with icon
\newcommand{\githublink}[1]{
	\faGithub\ \href{https://github.com/#1}{\textup{\protect\path{#1}}}
}

% Itemize bullets
\newcommand{\itemizeItem}{\item[\labelitemi]}


% CV Title
\colorlet{firstnamecolor}{lastnamecolor} % Make color of first and last names consistent
\name{Parmenion}{Koutsogeorgos}

\renewcommand{\emaillink}[1]{#1} % Fix email link
\email{\href{mailto:parmenkouts99@gmail.com}{parmenkouts99@gmail.com}}

\social[linkedin][linkedin.com/in/parmenion-koutsogeorgos-pk470/]{Parmenion Koutsogeorgos}
\social[github][github.com/pk-470]{pk-470}


% Document
\begin{document}


% Title
\makecvtitle


% Intro
\cvitem{}{
	I am an Artificial Intelligence Engineer based in the Netherlands. I am currently working part-time for Cordys Analytics, a startup affiliated with the University Medical Center Utrecht which applies A.I. methods for the purpose of diagnosing heart disease from electrocardiograms (ECGs). At the same time, I am working on my thesis for the Master of Science in Artificial Intelligence at Maastricht University, researching the use of State-Space models (Mamba) trained on bio-acoustic data for the purpose of monitoring animal populations. I have a strong background in Mathematics, having completed a bachelor's and master's in Mathematics at the University of Cambridge. I am mainly interested in A.I. with applications to engineering and healthcare.
}


% Professional experience
\section{Professional experience}

\cventry[1em]{Sep. 2024 - Today}{A.I. Engineer}{Cordys Analytics}{Utrecht, NL}{}{
    After completing a 6-month internship for Cordys Analytics, I started working with them as a part-time A.I. Engineer. My responsibilities involve both A.I. research work, as well as assistance with the development of the company's main software product, an end-to-end online diagnostic service.    	
}

\cventry[1em]{Mar. 2024 - Aug. 2024}{A.I. Intern}{}{}{}{
    During my internship, I focused on the topic of "Noise Detection and Uncertainty Estimation in ECGs," applying deep learning techniques to identify noisy electrocardiograms. My main contributions and takeaways include:
	\begin{itemize}
		\itemizeItem I familiarized myself with Out Of Distribution (OOD) detection methods and implemented various techniques from recent literature to improve the robustness and reliability of ECG noise detection models.
		\itemizeItem I designed and conducted various experiments, testing different models on public and private ECG datasets to evaluate and optimize the performance of noise detection algorithms.
		\itemizeItem I gained firsthand experience in the dynamic startup environment at Cordys.
		\itemizeItem I actively contributed to Cordy's ECGxAI package, a useful tool in the analysis and interpretation of ECG data using deep learning methods.
	\end{itemize}
	My strong performance and good work ethic during my internship resulted in me getting hired for a part-time A.I. Engineering role in the same company.
}

\cventry[1em]{Jul. 2024 - Aug. 2024}{Self-Learning Module Website Developer}{Maastricht University}{Maastricht, NL}{}{
    I developed and hosted on GitHub pages a self-learning module website template focused on Multivariable Calculus. I also wrote a Python script to convert LaTeX to HTML.
}

\cventry[1em]{Apr. 2023 - Feb. 2024}{Teaching Assistant}{}{}{}{
	I was a teaching assistant for bachelor's mathematics courses such as Linear Algebra, Logic, Probability \& Statistics and Multivariable Calculus.
}


% Education
\section{Education}

\cventry[1em]{Sep. 2022 - Today}{Master of Science in Artificial Intelligence}{Maastricht University}{Maastricht, NL}{}{
	I have taken courses in topics such as Search Algorithms, Deep Learning, Autonomous Robotics Systems, Computer Vision, Data Mining, Text Mining and Natural Language Processing. Additionally, as a part of my degree, I participated in two research group projects. I am currently working on my master's thesis alongside my work at Cordys Analytics.
}

\cventry[1em]{Oct. 2017 - Jul. 2021}{Master of Mathematics \normalfont{(bachelor's \& integrated master's)}}{University of Cambridge}{Cambridge, UK}{}{
	In my two final years of study I mainly focused on Logic and Combinatorics, taking courses such as: Model Theory (on which I wrote my master's thesis), Topics in Combinatorics, Ramsey Theory, Additive Combinatorics, Logic and Set Theory, Graph Theory. Other topics I have taken include: Differential Equations, Statistics, Linear Algebra, Number Theory, Group/Ring/Module Theory, Real and Complex Analysis, Topology, Probability and Measure Theory, Linear Analysis, Differential Geometry.
}

\cventry[1em]{Sep. 2014 - Jun. 2017}{Apolytirion of Geniko Lykeio \normalfont{(high-school diploma)}}{Mandoulides Schools}{Thessaloniki, GR}{}{
	Due to my strong performance in school exams as well as extracuriccular maths and physics competitions (most notably winning a bronze medal in the 18th Junior Balkan Mathematical Olympiad, a gold medal in the 31st Greek Junior National Mathematical Olympiad and the first place in the 25th Panhellenic Physics Competition) I received a full scholarship throughout my years of study in Mandoulides Schools.
}


% Skills
\section{Skills}

\cvitem[0.8em]{A.I. development}{
    I have practical experience in developing A.I. algorithms for signal analysis, including ECG and audio signals. Moreover, for my current master's I have studied and worked on high-quality projects in various fields of A.I., including Text Mining \& Natural Language Processing, Computer Vision and Robotics.
}

\cvitem[0.8em]{Python development}{
	I have extensive experience in Python, having used it for integration and evaluation of A.I. algorithms in production, for A.I. research, as well as for multiple university and personal projects. In particular, I am familiar with software development standards such as Object Oriented Programming and unit testing, as well as many libraries commonly used in machine learning, such as PyTorch, PyTorch Lightning, Scikit-learn, Pandas, Matplotlib, Numpy, etc. 
}

\cvitem[0.8em]{Problem solving \& mathematics}{
    Having completed the 4-year Mathematics course at the University of Cambridge, which includes the highly competitive Part III course (selective 4th year integrated master's), I have developed excellent problem solving skills. Moreover, I have a strong command of various pure and applied mathematical areas, including probability and statistics.
}

\cvitem[0.8em]{Communication skills}{
	My experiences working with a small multi-functional team in a startup and teaching courses from multiple faculties as a teaching assistant have helped me develop the ability to effectively communicate with people both on a technical and non-technical level.
}

\cvitem[0.8em]{Web development}{
    I have worked with HTML, CSS and JavaScript for personal projects as well as for developing a Self-Learning Module for the Multivariable Calculus course at the School of Business and Economics in Maastricht University. 
}

\cvitem[0.8em]{Linux \& bash scripting}{
    I have some experience with Linux and bash scripting, both as a power user as well as a developer.
}

\cvitem[0.8em]{MATLAB}{
    I have used MATLAB in multiple projects for my degree in Mathematics.
}


% Awards
\section{Awards}

\cventry[0.8em]{2022}{ACM AUTh Days of Coding}{Association for Computing Machinery (student chapter), Aristotle University of Thessaloniki}{}{First place}{Team competition. Our submissions: \githublink{pk-470/acm-auth-days-of-coding}}

\cventry[0.8em]{2016}{26th Panhellenic Physics Competition}{Hellenic Society for Physics, Science and Education}{}{Third Prize}{}

\cventry[0.8em]{2016}{33rd Greek National Mathematical Olympiad}{Hellenic Mathematical Society}{}{Silver Medal}{}

\cventry[0.8em]{2016}{Kangaroo Hellas Mathematical Competition}{Kangourou Sans Frontieres}{}{Distinction}{}

\cventry[0.8em]{2015}{American Mathematics Competition - AMC 10}{Mathematical Association of America}{}{Distinction}{
	Arrived in top 2.5\% internationally.
}

\cventry[0.8em]{2015}{4th Junior European Mathematical Cup}{Young Gifted Mathematicians Marin Getaldić}{}{Third Prize}{}

\cventry[0.8em]{2015}{32nd Greek National Mathematical Olympiad}{Hellenic Mathematical Society}{}{Silver Medal}{}

\cventry[0.8em]{2015}{25th Panhellenic Physics Competition}{Hellenic Society for Physics, Science and Education}{}{First Place}{}

\cventry[0.8em]{2014}{18th Junior Balkan Mathematical Olympiad}{Union of Mathematicians of Macedonia}{}{Bronze Medal}{}

\cventry[0.8em]{2014}{31st Greek Junior National Mathematical Olympiad}{Hellenic Mathematical Society}{}{Gold Medal}{}

\cventry[0.8em]{2013}{30th Greek Junior National Mathematical Olympiad}{Hellenic Mathematical Society}{}{Silver Medal}{}


% Maastricht projects
\section{Selected projects from my A.I.\ master's}

\cventry[1em]{Sep. 2022 - Jan. 2023}{Automatic Music Sheet Page Turner - \githublink{csotogd/Music-Score-Localization-2.0}}{}{}{}{
	Our group developed an algorithm with the aim to localize a recorded song snippet as played by a human within the music score of the entire song. Our algorithm is based on the one developed for the app Shazam, while also including techniques such as Monte-Carlo Robot Localization.
}

\cventry[1em]{Sep. 2022 - Oct. 2022}{Impasse AI - \githublink{pk-470/impasse-ai}}{}{}{}{
	I created a search engine for the game Impasse by Mark Steere which uses Alpha-Beta search along with move ordering, iterative deepening and a transposition table. When matched with the engines of my classmates in a tournament my engine came 3rd overall, surpassing many engines which could search deeper within the allowed time due to being written in languages faster than Python.
}


% Cambridge projects
\section{Selected computational projects from my Mathematics bachelor's}

\cventry[1em]{Mar. 2020 - Apr. 2020}{Graph Colouring}{}{}{}{
	I studied and implemented on MATLAB various techniques for efficiently bounding the chromatic number of a graph.
}

\cventry[1em]{Dec. 2019 - Jan. 2020}{Simulation of Random Samples from Parametric Distributions}{}{}{}{
	I used MATLAB to study and visualise the behaviour of random variables sampled from various distributions (exponential, gamma, normal, chi-squared).
}

\cventry[1em]{Mar. 2018 - Apr. 2018}{Ordinary Differential Equations}{}{}{}{
	I used MATLAB to study and compare three methods for solving ODEs (Leapfrog, Euler, RK4).
}


% Essays & Presentations
\section{Essays \& presentations}

\cventry[1em]{Feb. 2021 - Apr. 2021}{NIP Theories and O-minimality - \githublink{pk-470/nip-theories}}{Part III, University of Cambridge}{Cambridge, UK}{}{
	As a part of my master's in Mathematics I worked on an expository essay on Model Theory, a branch of Mathematical Logic. This essay required extensive literature review and study of multiple research publications, which I then had to combine in a unique way in order to create a coherent and focused text. The resulting work was graded to the standard expected of the introductory and literature review sections of a Ph.D. thesis. My final grade was 80/100.
}

\cventry[1em]{Feb. 2016 - Mar. 2016}{Inversion: Properties and Applications}{8th International Week Dedicated to Maths}{Thessaloniki, GR}{}{
	While still being a student in high school I independently worked on and presented a project on the properties of geometric inversion, and how it can be used to produce imaginative solutions to very hard competition problems.
}


% Extracurricular projects
\section{Extracurricular projects}

\cventry[1em]{2022}{Supermod - \githublink{pk-470/Supermod}}{}{}{}{
	In order to teach myself Python I created a Discord bot whose duties include fetching and manipulating data from Google spreadsheets, extracting and formatting data from messages, interacting with the users and making posts periodically.
}


% Languages
\section{Languages}

\cvitem{}{
	Greek (mother tongue), English (proficient), German (B1 level, can catch up if needed).
}


% Additional skills & interests
\section{Additional skills \& interests}

\cvitem[0.8em]{Rowing}{
	I was a member of the Emmanual College Boatclub in Cambridge and I rowed in the 2018 Fairbairn Cup.
}

\cvitem[0.8em]{Music}{
	For the past 7 years I have been playing and writing music for the electric bass (mainly) and the guitar.
}

\cvitem[0.8em]{\LaTeX}{
	I regularly use LaTeX to write technical and non-technical documents (including this one).
}


\end{document}